Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-24 manuscript/manuscript.tex
Minor changes in Theory

From equation \ref{eq:glq-var-dens} we can observe that the GLQ 
approximates the gravitational fields of a tesseroid as the ones 
generated by $N_\lambda N_\phi N_r$ point masses located at the nodes 
of the Legendre polynomials, where $N_i$ are the orders of the 
quadrature for each integration, with $i \in \{ \lambda, \phi, r \}$, 
in the same way as the GLQ works in the homogeneous density case.
Nevertheless, in this new variable density scenario, the information of 
the density function is summarised into the weights by taking into 
account only the values it assumes on those nodes.
Although this may sound discouraging, we intent to prove otherwise and 
show that this method, along with well suited discretization 
algorithms, approximates the gravitational fields with good accuracy.
\todo[inline]{no se si poner esta ultima oracion}

>>>>

From equation \ref{eq:glq-var-dens} we can observe that the GLQ approximates 
the gravitational fields of a tesseroid as the ones generated by $N_\lambda 
N_\phi N_r$ point masses located at the nodes of the Legendre polynomials, in 
the same way as the GLQ works in the homogeneous density case, where $N_i$ ($i 
\in \{ \lambda, \phi, r \}$) are the orders of the quadrature for each 
integration.
Nevertheless, in this new variable density scenario, the information of 
the density function is summarised into the weights by taking into 
account only the values it assumes on those nodes.
Although this may sound discouraging, we intent to prove otherwise and 
show that this method, along with well suited discretization 
algorithms, approximates the gravitational fields with good accuracy.
\todo[inline]{no se si poner esta ultima oracion}
